TacticToe: Learning to Prove with Tactics

### 2018-03-23 tactictoe_jv.tex
minor

\begin{abstract}
We implement a tactical prover TacticToe on top of the HOL4 interactive theorem
prover. TacticToe learns from human proofs which mathematical technique is
the most suitable in each proof situation.
This knowledge is then used by a Monte Carlo tree search algorithm to
explore the most promising tactic-level proof paths.
On a single CPU, with a time limit of 60 seconds, TacticToe proves 66.4\% of
7164 theorems in HOL4's standard library whereas
Eprover with auto-schedule solves 34.5\%. The success rate rises to 69.0\% by
combining the results of TacticToe and E~prover.
\end{abstract}

@@

We predict tactics through their associated goals. So, the features
for each kind of object can be extracted from different representations of
mathematical formulas. We start by describing features for \holfour terms. From
there, we extend the extraction mechanism
to goals, theorems and lists of goals. Duplicated features are always removed
so that each object has an associated set of features.

Here are the kinds of features we extract from terms:
\begin{itemize}
\item names of constants, including the logical operators,
\item type constructors present in the types of constants and variables,
\item subterms with all variables replaced by a single placeholder $V$,
\item names of the variables.
\end{itemize}
Goals (respectively theorems) are represented by pairs consisting of a list of
terms (assumptions) and a term (conclusion). We distinguish between
features of the assumptions and features of the conclusion by adding a
different tag to elements of each set. The feature of a goal (respectively
theorem)
are the union of all these tagged features. From
that, we can construct features for a list of goals by computing the union of
the features of each goal in the list.

>>>>

\begin{abstract}
We implement a tactical prover TacticToe on top of the HOL4 interactive theorem
prover. TacticToe learns from human proofs which mathematical technique is
the most suitable in each proof situation.
This knowledge is then used by a Monte Carlo tree search algorithm to
explore the most promising tactic-level proof paths.
On a single CPU, with a time limit of 60 seconds, TacticToe proves 66.4\% of
7164 theorems in the HOL4's standard library whereas
Eprover with auto-schedule solves 34.5\%. The success rate rises to 69.0\% by
combining the results of TacticToe and E~prover.
\end{abstract}

@@

We predict tactics through their associated goals. So, the features
for each kind of object can be extracted from different representations of
mathematical formulas. We start by describing features for \holfour terms. From
there, we extend the extraction mechanism
to goals, theorems and lists of goals. Duplicated features are always removed
so that each object has an associated set of features.
Here are the kinds of features we extract from terms:
\begin{itemize}
\item names of constants, including the logical operators,
\item type constructors present in the types of constants and variables,
\item subterms with all variables replaced by a single placeholder $V$,
\item names of the variables.
\end{itemize}
Goals (respectively theorems) are represented by pairs consisting of a list of
terms (assumptions) and a term (conclusion). We distinguish between
features of the assumptions and features of the conclusion by adding a
different tag to elements of each set. The feature of a goal (respectively
theorem)
are the union of all these tagged features. From
that, we can construct features for a list of goals by computing the union of
the features of each goal in the list.
